\documentclass[12pt]{exam}

\input{../CMPreamble.tex}

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Midterm 2A}
\newcommand{\TestDate}{June 2019}
% \newcommand{\TestTime}{} % QUP
\newcommand{\TestTime}{10:05 am to 11:20 am}
\newcommand{\Duration}{75  }
\newcommand{\Points}{50 }


\begin{document}
    
\input{../CMCoverPage}

\newpage \InitialsRight

% QUP EXAM
\begin{questions}

    \question[10] 
    Use the method of reduction of order to find a second solution, $y_2$, to the DE so that $\{y_1,y_2\}$ forms a fundamental set. $$ y'' - \frac 1t y' + \frac{1}{t^2}y = 0, \quad t>0, \quad y_1(t) = t$$


    \newpage \InitialsLeft \\ \Scratch 

    
    \newpage    \InitialsRight
    
        \question[9] Consider the system of equations. 
        $$
        x_1 ' = 3x_1 -2x_2 + 4x_3, \qquad x_2 ' = -2x_1 + 6x_2 + 2x_3 , \qquad x_3 ' = 4x_1 + 2x_2 + 3x_3 
        $$
        \begin{enumerate} 
            \item[a)] Express the system of equations in the form $\vec x \, ' = A \vec x$. \vspace{3cm} 

            \item[b)] Determine the eigenvectors of $A$ and write down the general solution. You may use that the only eigenvalues of $A$ are $7$ and $-2$. 
                
        \end{enumerate}
        
    \newpage \InitialsLeft
    \Scratch 
        

    \newpage \InitialsRight
    
    \question[10] A 4 kg mass stretches a spring 0.1 meters. The mass is pushed upward, contracting the spring a distance of 0.1 meters, and then set in motion with a downward velocity of 2 m/s. There is no damping. 
    \begin{parts} \part[6] Solve the IVP. You may use that the acceleration due to gravity is $g = 10$ m/s$^2$. \vspace{9cm} \part[1] What is the frequency of the motion? It is not necessary to specify units. \vspace{1cm} \part[3] Sketch the phase portrait for this system. Include the trajectory, $\vec r(t)$, in the phase portrait that corresponds to the initial conditions. Clearly label this trajectory and do not forget to label your axes.  \end{parts} 

    \newpage \InitialsLeft

    \question[2] Determine all values of $\alpha$, if any, for which all solutions tend to zero as $t\to\infty$. $$y'' - (2\alpha - 1) y' + (\alpha^2-\alpha+1) y = 0, \quad \alpha \in \mathbb R$$ \vspace{5cm}  % 4.3.47
    
    
    % \question[2] % 6.3.4
    % State the largest possible interval on which solutions to the IVP are certain to exist. Do not solve the DE.  $$(t-2)y'''+ty''+5t^2y'+2t^3y = \ln t, \quad y(1) = 1$$. \vspace{3cm}
    
    \question[3] Consider a one-dimensional lattice consisting of $3$ lattice points, as in the figure.
    
        \begin{center}
            \begin{tikzpicture}
                \begin{scope}[<->,>=stealth',shorten >=1pt,auto,node distance=1.75cm,thick, main node/.style={circle,fill=gray!10,draw}]
                \node[main node] (1) {$x_1$};
                \node[main node] (2) [right of=1] {$x_2$};
                \node[main node] (3) [right of=2] {$x_3$};
                \path[every node/.style={font=\sffamily\small}]
                (1) edge node[below] {} (2)
                (2) edge node [above] {} (3);
                \end{scope}
            \end{tikzpicture}  
        \end{center}  
        
        Let $x_j(t)$ be the number of particles residing at the $j$th lattice point at time $t$. Assume that $x_j$ satisfies the following rate equations.
        \begin{align*} 
            \frac{dx_1(t)}{dt} = k(x_2 - x_1) , \quad 
            \frac{dx_2(t)}{dt} = k(x_3 - 2 x_2 + x_1 ) , \quad 
            \frac{dx_3(t)}{dt} = kx_2 
        \end{align*} 
        Assume $k \in \mathbb R$, $k \ne 0$, and $t \ge 0$. Determine whether the total number of particles in the system is constant. 


    \newpage \InitialsRight
    \question[6]  Determine a suitable form for the particular solution, $Y(t)$, to the differential equations if the method of undetermined coefficients is to be used. Do not determine the values of the coefficients or solve the differential equations. 
    \begin{parts}
        \part $y'' + 4y = t^2 + \sin(2t)$ \vspace{8cm}
        \part $y'' +2y' - 3y = 3te^t\sin t$
    \end{parts} 

    \newpage \InitialsLeft


    \question[10] Use variation of parameters to identify the general solution to $$t^2 y'' - t(t+2)y' + (t+2)y = 5t^3, \quad t > 0$$ Solutions to the corresponding homogeneous equation are $y_1(t) = t$, $y_2(t) = te^t$.
    

    
    
\end{questions}
    
\newpage \LastPage 


\end{document}

