

% SETTING WEEKLY OR DAILY GOALS



% SCHEDULING TIME



% MANY PRACTICE PROBLEMS



% PACE: SPREAD STUDYING OUT 




% Other Great Ideas 

These were important to me so that I would be able to keep my sanity and have a balance of school.
They are important because they will help me make an A while keeping my health in check.
I'm a math major, so going forward, I will need to retain and apply foundational information in my proofs, research, etc
These goals are important to me because I would like to see much growth compared to the end of Spring 2020 to the end of Summer 2020 where I can confidently enter a class with a mindset and procedure I can follow that will make sure I fully understand what is going on in my classes. And also an A would be very nice.
I believe math is important for me in the future no matter which engineering field I will work with.
Understanding diff eqs is important to me as I hear they are very useful in my major (Computer Engineering) to model certain electrical systems.  Because I want to do cool stuff with electronics, I probably need to know some diff eqs.

% APPLICATIONS



% Connecting with others


% TEXTBOOK
Read the textbook from start to finish and work through a bunch of practice problems.



% MAKING USE OF AVAILABLE RESOURCES





















I completed my assignments far in advance of when they were due, and consulted with professors and classmates about problems I did not understand prior to exams.
What I did is set a general schedule and force myself to stick to those. Fortunately, one of my classes has a set lecture time, so right now I'm basing my daily plan based on that.
I hopefully executed what I stated in the first question and did not slack off from doing them. I also want to make it to at least one TA/professor office hours. 
Watch all lectures, read textbook, complete all assignments, go to office hours


, distributing lectures, recitations worksheets, homeworks, and study time for tests and quizzes.
I'm going to set reminders for office hours and adjust my calendar so my deadlines are in there and .
I kept a rigid schedule for studying and completing assignments. I reached out to professors and other students for assistance and clarification. I kept a review schedule all semester to prepare myself for exams.
To reach these goals, I hope that I will stay engaged and on schedule in the course, find a study group, go to office hours, and look for outside resources if needed to help me do well in the course. 


