\documentclass[12pt]{exam}

\usepackage{graphicx} % allows for graphics
\usepackage{ifthen}  % for if statements 

\newcommand{\sol}{0} %solution =1 or 0

\input{preamble.tex}

% COLORS FOR DIAGRAMS
\definecolor{DarkBlue}{rgb}{0.0,0.0,0.6} % 
% \definecolor{DarkGreen}{rgb}{0.0,0.3,0.0} % 
% \definecolor{DarkRed}{rgb}{0.6,0.0,0.0} % 

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Midterm 2}
\newcommand{\TestTime}{}
\newcommand{\Duration}{12 hours }
\newcommand{\Points}{}
% \newcommand{\DueDate}{12:30 PM ET}
\newcommand{\DueDate}{8:00 PM ET}


% \usepackage{tikz}
% \usetikzlibrary{shapes,snakes}   
% \usetikzlibrary{arrows,automata}

\begin{document}
    

\input{2021Spr/coverpage} % cover page for unproctored exam

\newpage


\Initials

\begin{questions}

    \question[2] Determine all values of $\alpha$, if any, for which all solutions tend to zero as $t\to\infty$. $$y'' - \ldots , \quad \alpha \in \mathbb R$$ \vspace{4cm}  
    
    \question[2] Determine whether the functions $y_1 = $ and $y_2 = $ are a fundamental set of solutions to the differential equation $y''+Xy'+Yy = 0$ with $y=y(t)$. 
    
    \vspace{6cm}
    
    \question[2] Construct an initial value problem for the following situation. 

    \begin{itemize}
        \item[] A spring is stretched X m by a force of Y newtons (N). A mass weighing Z kg is attached to a spring that is also attached to a viscous damper that applies a force of NUMBER Newtons when the velocity of the mass is NUMBER m/s. The mass is pulled down XX m below its equilibrium position and given an initial upward velocity of YY m/s. 
    \end{itemize}
    
    \question[1] State whether the following differential equation is linear or non-linear, homogeneous or non-homogeneous, and whether it is autonomous or not autonomous. 
    $$4y'' + (1-y)y' + 2y =0 $$
    
    \question[2] If $W[f, g]$ is the Wronskian of $f$ and $g$, and if $u=4f+g, \ v=3f-2g$, find the Wronskian $W[u,v]$ of $u$ and $v$ in terms of $W [ f , g]$.
    
    \question[4] Solve the IVP.
    $$y''+xy'+xy=0,\quad y(0)=2,\ y'(0)=-2$$
    
    \question[4] Determine a suitable form for the particular solution \(Y(t)\) if the method of undetermined coefficients is to be used. 
    $$y''+ $$
    
    \newpage 

    \question[8] Use the variation of parameters method to identify the general solution to \[\vec{x} \, ' = \left( \begin{array}{rr} x & x \\ x & x \end{array} \right) \vec{x}  + \left( \begin{array}{r}  x \\ x \end{array} \right)  \]
    
    A solution to the corresponding homogeneous equation is $y_h = c_1e^{-xt}\spalignmat{x;-x}+c_2e^{xt}\spalignmat{x;x}$.


    \newpage
    \question[2] A small number of points will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{enumerate}
        % \item your scan is under 5 MB in file size
        \item your work is legible in the scan
        \item your name or initials are at the top of every page
        \item questions are answered in the order in which they were given
        \item during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{enumerate}
    Ensuring that these criteria are met helps ensure that your exam is graded efficiently and accurately. 
    


    
\end{questions}
    
    Please sign and date the following GT Honor Code statement. \\ 
    
    \vspace{6pt}
    \textbf{Georgia Tech Honor Code}\\
    \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    
\end{document}

