\documentclass[12pt]{exam}

\usepackage{graphicx} % allows for graphics
\usepackage{ifthen}  % for if statements 

\newcommand{\sol}{0} %solution =1 or 0

\input{preamble.tex}

% COLORS FOR DIAGRAMS
\definecolor{DarkBlue}{rgb}{0.0,0.0,0.6} % 
% \definecolor{DarkGreen}{rgb}{0.0,0.3,0.0} % 
% \definecolor{DarkRed}{rgb}{0.6,0.0,0.0} % 

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Midterm 1}
\newcommand{\TestTime}{}
\newcommand{\Duration}{12 hours }
\newcommand{\Points}{}
% \newcommand{\DueDate}{12:30 PM ET}
\newcommand{\DueDate}{8:00 PM ET}


% \usepackage{tikz}
% \usetikzlibrary{shapes,snakes}   
% \usetikzlibrary{arrows,automata}

\begin{document}
    

\input{2021Spr/coverpage} % cover page for unproctored exam

\newpage


\InitialsRight

\begin{questions}

    \question[2] Convert the DE to a first order system. Express your system in the form $\vec x \, ' = A\vec x +\vec b$. 
    $$y''-ty'+400y = \cos(t)$$
    
    \vspace{6cm}
    
    \question[1] For what values of $t$ are solutions to the IVP certain to exist? $$\sqrt{36-t^2} \, \dydt + t y = \cos t, \quad y(1) = 0$$.
    
    \vspace{4cm}
    
    \question[2] Consider the DE $y''+ y = t^3$.
    \begin{parts}
        \part State whether the DE is linear or non-linear. \vspace{1cm}
        \part State whether the DE is homogeneous or non-homogeneous. \vspace{1cm}
        \part State whether the DE is autonomous or non-auntonomous. \vspace{1cm}
        \part What is the order of the DE? \vspace{1cm}
    \end{parts}
    
    \newpage 

    \question[6]  Newton’s law of cooling states that the temperature of an object changes at a rate proportional to the difference between its temperature and that of its surroundings. Suppose that the temperature of a cup of coffee obeys Newton’s law of cooling. The coffee has a temperature of 200F when freshly poured and is in a room whose temperature is changing. The temperature of the room is given by $70+t$, where $t$ is measured in hours. 
    \begin{parts}
        \part Construct an IVP to model this situation. 
        \vspace{6cm}
        \part Solve your IVP. Express your solution in explicit form. Show your work.
    \end{parts}
    


    \newpage 
    
    \question[10] %2.5.11 verbatim 
    Consider the differential equation $\displaystyle \dydt = k(y-1)(y-9)$, where $y$ is a real function of $t$, and $t \ge 0$, and $k>0$. 
    \begin{parts}
        \part State the critical points of the differential equation.  \vspace{1cm} 
        \part Draw the phase line, and determine whether the critical points (if any) are stable, semi-stable, or unstable. Show your work. 
        \vspace{6cm}
        \part Determine where $y$ is concave up and where $y$ is concave down for all $y \ge 0$.  Show your work. 
        \vspace{6cm}
        \part Using results from parts (a), (b), and (c) to sketch several solution curves in the $ty$-plane for $y \ge 0$ and $t \ge 0$.
    \end{parts}
    
    \newpage 
    
    \question[3]  Consider the system $$\vec x \, ' = A\vec x, \quad A = \begin{pmatrix} -5&4\\-4&-5 \end{pmatrix}, \quad \vec x = \begin{pmatrix} x(t)\\y(t)\end{pmatrix} $$ The eigenvalues of $A$ are $\lambda = -5\pm 4i$. Sketch the phase portrait of the system. Please indicate the direction of motion on your solution curves and label your axes.     
    \vspace{6cm}
    \question[2] Consider the equation $\dydt = (y-1)(y-k)$ Assume $k$ can be any real number. 
    Draw the bifurcation diagram. That is, plot the location of the critical points versus $k$.
    \vspace{5cm}
    
    \newpage
    
    \question[10] Consider the system $\displaystyle \vec x \, ' = A \vec x =  \begin{pmatrix} -1&2\\2&2 \end{pmatrix} \vec x$, where $\vec x = \vec x(t)$. 
 	
    \begin{parts}
        \part[2] Determine the eigenvalues of $A$. Show your work. \vspace{6cm}

        \part[5] Express the general solution of the system in terms of real valued functions. Show your work. 
        \vspace{9cm} 
        % \newpage 
        \part[3] Sketch the phase portrait of the system. Please include the eigenspaces in your sketch, indicate the direction of motion of your solution curves and eigenspaces, and do not forget to label your axes.      
        % \vspace{4cm} 
    \end{parts}
    
    \newpage 
    
    \newpage
    \question[3] In the system below the coefficient matrix contains a parameter, $k$.  
    
    $$\vec x \, ' = \begin{pmatrix} 1&-5\\ k & -1\end{pmatrix} \vec x$$

    \begin{parts}
    \part Determine the eigenvalues in terms of $k$. \vspace{5cm}
    \part Identify the critical value or values of $k$ where the qualitative nature of the phase portrait for the system changes. 
    \end{parts}

    
    
    \newpage

    \question[1] A small number of points will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{enumerate}
        % \item your scan is under 5 MB in file size
        \item your work is legible in the scan
        \item your name or initials are at the top of every page
        \item questions are answered in the order in which they were given
        \item during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{enumerate}
    Ensuring that these criteria are met helps ensure that your exam is graded efficiently and accurately. 
    

    
\end{questions}
    
    Please sign and date the following GT Honor Code statement. \\ 
    
    \vspace{6pt}
    \textbf{Georgia Tech Honor Code}\\
    \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    
\end{document}