\documentclass[12pt]{exam}

\input{2021Sum/preamble}

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Quiz 3}
\newcommand{\TestDate}{}
\newcommand{\DueDate}{the due date indicated in the syllabus}
\newcommand{\TestTime}{8:15 pm to 9:15 pm}

\begin{document}
    
\input{2021Sum/coverpage}

\newpage

\begin{questions}

\question[5] Use the method of reduction of order to find a second solution, $y_2$, to the DE so that $\{y_1,y_2\}$ forms a fundamental set. $$ t^2y'' +8t y' - 18y = 0, \quad t>0, \quad y_1(t) = t^2$$. 

\newpage 
\question[5] Consider the DE $$y''-4y'+5y = 0$$
\begin{parts}
    \part Solve the DE. \vspace{10cm}
    \part Classify the critical point of the corresponding dynamical system according to type (node, spiral, saddle, etc) and stability. \vspace{2cm}
    \part Sketch the phase portrait of the system. Include in your diagram straight-line orbits (if any). Please label your axes. Indicate the direction of motion on your solution curves. 
    
\end{parts}
    
\newpage

\question[4] If the Wronskian, $W$, of $f(t)$ and $g(t)$ is $e^{\omega t}$, and if $f(t) = e^{kt}$, determine $g(t)$. You can assume $k>0$ and $\omega>0$. And you can leave your answer in terms of $\omega$ and $k$. Show your work. 

\newpage 

\question[3] A spring is stretched 40 cm by a force of 20 newtons (N). A mass of 2 kg is then hung from the same spring and is also attached to a viscous damper that exerts a force of 3 N when the velocity of the mass is 12 m/s. The mass is pulled down 2 cm below its equilibrium position and given an initial downward velocity of 40 cm/s. Write down the IVP based on this physical description. You do not need to solve your IVP. 

\vspace{8cm}

\question[2] Give an example of a constant coefficient differential equation whose general solution is $y = c_1 e^{-5t} + c_2 e^{-4t}$. You do not need to show your work for this question, you can just write down your differential equation. 





\newpage



\question[1] A small number of points will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{parts}
        % \item your scan is under 5 MB in file size
        \part your work is legible in the scan
        \part questions are answered in the order in which they were given
        \part during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{parts}
    Ensuring that these criteria are met helps ensure that your work is graded efficiently and accurately. 

\end{questions}
\vspace{2cm}
    
    \vspace{6pt}
    \textbf{Georgia Tech Honor Code}\\
    \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    

\end{document}