\documentclass[12pt]{exam}

\input{2021Sum/preamble}

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Quiz 2}
\newcommand{\TestDate}{}
\newcommand{\DueDate}{the due date indicated in the syllabus}
\newcommand{\TestTime}{8:15 pm to 9:15 pm}

\begin{document}
    
\input{2021Sum/coverpage}

\newpage

\begin{questions}

\question[6] Consider the first order linear system of differential equations $\vec x \, ' = A\vec x$, where $\vec x = \vec x(t)$, and $$A = \begin{pmatrix} 2&0&0\\0&4&1\\0&1&4\end{pmatrix}$$
The eigenvalues of $A$ are $\lambda_1 = 2$, $\lambda_2 = 3$, and $\lambda_3 = 5$. 
\begin{parts}
    \part Determine the eigenvectors of $A$. Please show your work. 
    \vspace{14cm}
    \part Write down the general solution to the system of differential equations using your results from part (a). 
\end{parts}

\newpage 

\question[4] Consider the first order constant coefficient linear system of differential equations $\vec x \, ' = A\vec x$, where $\vec x = \vec x(t)$. The eigenvalues and eigenvectors of $A$ are as follows. $$\lambda_1 = -4, \ \vec v_1 = \begin{pmatrix}1\\0\\1 \end{pmatrix} , \quad \lambda_2 = -4, \ \vec v_2 = \begin{pmatrix} 8\\4\\9 \end{pmatrix}, \quad \lambda_3 = -12, \ \vec v_3 = \begin{pmatrix} 0\\1\\1\end{pmatrix}$$
Write down the general solution to the system of differential equations.



\newpage

\question[4] Consider the fourth order differential equation. 
$$2y^{(4)}-4y=12\cos(t)$$
Express the differential equation as a first order system in the form $\vec x \, ' = A \vec x + \vec b$. 

\newpage 

\question[5] Consider the first order linear system of differential equations $\vec x \, ' = A\vec x$. The eigenvalues and eigenvectors of $A$ are as follows. $$\lambda_1 = -2, \ \vec v_1 = \begin{pmatrix}1\\0\\1 \end{pmatrix} , \quad \lambda_2 = 3i, \ \vec v_2 = \begin{pmatrix} 1+2i\\1+3i\\2 \end{pmatrix}, \quad \lambda_3 = -3i, \ \vec v_3 = \begin{pmatrix} 1-2i\\1-3i\\2\end{pmatrix}$$
Write down the general solution to the system of differential equations in terms of real-valued functions. 

\newpage



\question[1] A small number of points will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{parts}
        % \item your scan is under 5 MB in file size
        \part your work is legible in the scan
        \part questions are answered in the order in which they were given
        \part during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{parts}
    Ensuring that these criteria are met helps ensure that your work is graded efficiently and accurately. 

\end{questions}
\vspace{2cm}
    
    \vspace{6pt}
    \textbf{Georgia Tech Honor Code}\\
    \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    

\end{document}