\documentclass[12pt]{exam}

\input{2021Sum/preamble}

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Quiz 1}
\newcommand{\TestDate}{}
\newcommand{\DueDate}{the due date indicated in the syllabus}
\newcommand{\TestTime}{8:15 pm to 9:15 pm}

\begin{document}
    
\input{2021Sum/coverpage}

\newpage

\begin{questions}

    \question[4] Consider the IVP. $$\dydt = 40t e^{-4y}, \quad y(2) = 0$$
    \begin{parts}
        \part Determine a solution to the IVP in explicit form. Show your work.\vspace{10cm}
        \part For what values of $t$ is the solution to the IVP defined? 
    \end{parts}

\newpage
    \question[2] Consider the DE. $$\dydt + y^2 = t+1$$
    \begin{parts}
        \part State whether the DE is linear or non-linear. \vspace{2cm}
        \part What is the order of the DE? \vspace{2cm}
    \end{parts}
    
    \question[3] List all values of $r$ so that $y=e^{rt}$ is a solution to $y'' - 9y'+20y=0$, where $y=y(t)$. Assume that $r\in \mathbb R$ and $y$ is not a function of $r$. Show your work. 
% ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  
\newpage 

    \question[10] % 
    Consider the differential equation $\displaystyle \dydt = -(y-k)^2(y-2)$, where $y$ is a real function of $t$, and $t \ge 0$, and $0<k<1$. 
    \begin{parts}
        \part State the critical points of the differential equation.  \vspace{1cm} 
        \part Draw the phase line, and determine whether the critical points (if any) are stable, semi-stable, or unstable. Show your work. 
        \vspace{8cm}
        \part Using results from parts (a) and (b) to sketch several solution curves in the $ty$-plane for $t \ge 0$.
    \end{parts}
    
    
\newpage
\question[1] A small number of points will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{parts}
        % \item your scan is under 5 MB in file size
        \part your work is legible in the scan
        \part questions are answered in the order in which they were given
        \part during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{parts}
    Ensuring that these criteria are met helps ensure that your work is graded efficiently and accurately. 

\end{questions}
\vspace{2cm}
    
    \vspace{6pt}
    \textbf{Georgia Tech Honor Code}\\
    \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    

\end{document}


