\documentclass[12pt]{exam}

\input{2021Sum/preamble}

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Sample Quiz 3}
\newcommand{\TestDate}{2018}
\newcommand{\DueDate}{the due date indicated in the syllabus}
\newcommand{\TestTime}{8:30 am to 8:50 am}

\begin{document}
    
\input{2021Sum/coverpage}

\newpage

\begin{questions}



%% ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~  ~ ~ ~ ~ 

    \newpage
    \question[4] A spring is stretched 0.5 m by a force of 0.25 newtons (N). A mass weighing 2 kg is attached to a spring that is also attached to a viscous damper that applies a force of 10 N when the velocity of the mass is 5 m/s. The mass is pulled down 2 m below its equilibrium position and given an initial upward velocity of 4 m/s. Construct an initial value problem for this  situation. % from 2018 quiz 3 
    
    \newpage
    \question[6] Use the reduction of order to find a second solution $y_2$ of the given differential equation such that $\{ y_1 , y_2 \}$ is a fundamental set of solutions on the given interval. $$ t^2y''-4ty'+6y = 0, \quad t > 0, \quad y_1=t^2
    $$ % 4.2#29
    
    \newpage
    \question[3]
    Determine all values of $\alpha$ for which all solutions tend to zero as $t \to \infty$. $$y''-(2\alpha -3)y'+\alpha(\alpha-3)y = 0$$ %4.3 #47
    
    \newpage
    \question[6] Find the general solution to the DE $9y''+6y'+y=0$. Classify the critical point of the corresponding dynamical system in terms of stability and type. Sketch the phase portrait of the system. If the eigenvalues are real please include the eigenspaces in your sketch, indicate the direction of motion of your solution curves and eigenspaces, and do not forget to label your axes.  % 4.3 #4
    
    

\newpage

    \question[1] A small number of points will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{parts}
        % \item your scan is under 5 MB in file size
        \part your work is legible in the scan
        \part questions are answered in the order in which they were given
        \part during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{parts}
    Ensuring that these criteria are met helps ensure that your work is graded efficiently and accurately. 

\end{questions}

   Please sign and date the following GT Honor Code statement. \\ 
    
    \vspace{6pt}
    \textbf{Georgia Tech Honor Code}\\
    \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    

\end{document}

