\documentclass[12pt]{exam}

\usepackage{graphicx} % allows for graphics
\usepackage{ifthen}  % for if statements 

\newcommand{\sol}{0} %solution =1 or 0

\input{../preamble.tex}

% COLORS FOR DIAGRAMS
\definecolor{DarkBlue}{rgb}{0.0,0.0,0.6} % 
% \definecolor{DarkGreen}{rgb}{0.0,0.3,0.0} % 
% \definecolor{DarkRed}{rgb}{0.6,0.0,0.0} % 

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Midterm 2M}
\newcommand{\TestTime}{}
\newcommand{\Duration}{3 hours }
\newcommand{\Points}{}
\newcommand{\DueDate}{12:30 PM ET}


% \usepackage{tikz}
% \usetikzlibrary{shapes,snakes}   
% \usetikzlibrary{arrows,automata}

\begin{document}
    

\input{../CoverCovid.tex} % cover page for unproctored exam

\newpage


\InitialsRight

\begin{questions}

    \question[8] 
    Use the method of reduction of order to ﬁnd a second solution $y_2$ of the given diﬀerential equation such that $\{ y_1 , y_2 \}$ is a fundamental set of solutions on the given interval.
    
    $$t^2y'' - 3ty' + 3y = 0, \quad t > 0, \quad y_1(t) = t$$
    
    \newpage    \InitialsLeft
    
        \question[9] Consider a lattice with $3$ lattice points, as in the figure below. 
    
        \begin{center}
            \begin{tikzpicture}
                \begin{scope}[<->,>=stealth',shorten >=1pt,auto,node distance=1.75cm,thick, main node/.style={circle,fill=gray!10,draw}]
                \node[main node] (1) {$x_1$};
                \node[main node] (2) [right of=1] {$x_2$};
                \node[main node] (3) [right of=2] {$x_3$};
                \path[every node/.style={font=\sffamily\small}]
                (1) edge node[below] {} (2)
                (2) edge node [above] {} (3);
                \end{scope}
            \end{tikzpicture}  
        \end{center}  
        
        Let $x_j(t)$ be the number of particles residing at the $j$th lattice point at time $t \ge 0$. Assume that $x_j$ satisfies the following rate equations.
        \begin{align*} 
            \frac{dx_1(t)}{dt} = x_2 - x_1 , \qquad 
            \frac{dx_2(t)}{dt} = x_3 - 2 x_2 + x_1 , \qquad \frac{dx_3(t)}{dt} = x_3
        \end{align*} 
        % Answer the following questions.
        \begin{enumerate} 
            \item[a)] Express the system of equations in the form $\vec x \, ' = A \vec x$. 
                \vspace{2cm}

                \item[b)] Determine the eigenvectors of $A$ and write down the general solution to $\vec x \, ' = A\vec x$. You may use that the eigenvalues of $A$ are $0, 1$ and $-3$. 
                \vspace{10cm} 
                \item[c)] What does the solution converge to as $t \to \infty$? 
        \end{enumerate}
        
        
        
    \newpage \InitialsLeft
        
    \question[10] The position of an undamped spring-mass system satisfies the IVP $$y'' + 5y = 0, \quad y(0) = -1, \quad y'(0) = 0$$ \begin{parts} \part Solve the IVP. \vspace{5cm} \part Sketch the component plot for $y(t)$. \vspace{3cm} \part Sketch the phase portrait for this system. Include the trajectory, $\vec r(t)$, that corresponds to the initial conditions. Clearly label this trajectory and do not forget to label your axes.  \end{parts} 
    
    \newpage \InitialsRight
    
    \question[2] Determine all values of $\alpha$, if any, for which all solutions tend to zero as $t\to\infty$. $$y'' - (2\alpha - 1) y' + (\alpha^2-\alpha+1) y = 0, \quad \alpha \in \mathbb R$$ \vspace{5cm}  % 4.3.47
    
    
    \question[2] % 6.3.4
    State the largest possible interval on which solutions to the IVP are certain to exist. $$(t-2)y'''+ty''+5t^2y'+2t^3y = \ln t, \quad y(1) = 1$$.
    \vspace{3cm}
    

    \newpage \InitialsLeft
    \question[7]  Determine a suitable form for the particular solution, $Y(t)$, to the differential equations if the method of undetermined coefficients is to be used. Do not determine the values of the coefficients or solve the differential equations. 
    \begin{parts}
        \part $y'' - 2y' - 3y = (t^2 + 1)e^{-t}$ \vspace{8cm}
        \part $y'' +2y' - 3y = 3te^t\sin t$
    \end{parts}
    


    \newpage \InitialsRight
    \question[10] Use the variation of parameters method to identify the general solution to \[\vec{x} \, ' = \left( \begin{array}{rr} 2 & 3 \\ 3 & 2 \end{array} \right) \vec{x}  + \left( \begin{array}{r}  0\\ 1\end{array} \right)  \]

    
    \newpage 

    \question[2] A small number of points will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{enumerate}
        % \item your scan is under 5 MB in file size
        \item your work is legible in the scan
        \item your name or initials are at the top of every page
        \item questions are answered in the order in which they were given
        \item during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{enumerate}
    Ensuring that these criteria are met helps ensure that your exam is graded efficiently and accurately. 
    


    
\end{questions}
    
    Please sign and date the following GT Honor Code statement. \\ 
    \vspace{2pt}
    
    \textbf{Georgia Tech Honor Code}:\ \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    
\end{document}
