%%%%% Problems %%%%%


\item
(a) Find the general solutions of 
$\displaystyle {dy\over dt}+10t^4 y= 50 t^9 e^{3t^5}.$ 

(b) Solve the initial value problem $\displaystyle
{dy\over dt}+10t^4 y= 50 t^9 e^{3t^5}, y(0)=-1.
$ 

\item
Solve the initial value problem
$\displaystyle {dx\over dt}= x^2 e^{-2t},  \quad x(0)=3$.

\item
A tank initially contains 100~gallons of brine with 10~lb
of salt dissolved in it. 
Brine containing 0.4~lb of salt per gallon flows from an outside source into the tank at a rate of 5~gal/min. 
The mixture is discharged out of the tank at the same rate of 5~gal/min.. 
Assume that solutions are well-stirred at all times. 
	\begin{enumerate}
	\item
Write the initial value problem for $Q(t)$.
	\item
Find the amount $Q(t)$ of salt in the tank at time $t\ge 0$.
	\item
Find the limit of $Q(t)$ as $t\to\infty$.
	\end{enumerate} 


\item 
Suppose that a population is 12 millions presently, 
and that the annual growth rate of the population is constantly 2 percent.
Denote by $P(t)$ the population after $t$ years.
	\begin{enumerate}
	\item
Write the initial value problem for $P(t)$.
	\item
Find $P(t)$ by solving the initial value problem.
	\item
When will the population double?
	\end{enumerate}


\item
A 4-lb roast, initially at $50^{\circ}\mbox{F}$, is placed in a $375^{\circ}\mbox{F}$ oven at 5:00pm.
After 75 minutes it is found that the temperature of the roast is $125^{\circ}\mbox{F}$.
	\begin{enumerate}
	\item
Write the initial value problem for $T(t)$, the temperature of the roast after $t$ minutes.
	\item
Find $T(t)$ by solving the initial value problem.
	\item
When will the roast be $150^{\circ}\mbox{F}$ (medium rare)?
	\end{enumerate}


\item 
A baseball is thrown vertically up. 
After it reaches the heighest
point, it starts to fall down.

Assume that the force of air resistance is 
$mgv^2/v_T^2$~Newtons, where mass $m$ is measured in kg, 
the gravitational acceleration $g=9.8~\mbox{\rm m}/\mbox{\rm s}^2$,
the velocity $v$ is measured in m/s,
and $v_T$ is the terminal speed: $v_T=40$~m/s for a baseball.

Let the upward velocity be positive velocity.

	\begin{enumerate}
	\item
Write down a differential equation for the velocity $v(t)$
when the ball is rising up.
	\item
Write down a differential equation for the velocity $v(t)$
when the ball is falling down.
	\end{enumerate}

\item
Consider the equation $\displaystyle {dy \over dt}= -0.5 y^2 (y^2+1) (y^2 -4)(y+1) e^{\sin y} .$
	\begin{enumerate}
	\item
Find all equilibrium solutions.
	\item
Sketch the phase portrait.
	\item
Determine whether each equilibrium is stable, asymptotically stable, or unstable.
	\end{enumerate} 

\def\one_dim_lin_approx{
\item
Consider the equation $\displaystyle {dy \over dt}= \frac{1}{16} (y+1)^3 (y-2)^2 (-y^3+y^2+6y).$
	\begin{enumerate}
	\item
Find all equilibrium solutions.
	\item
For each equilibrium point, write down the linear approximating equation near the equilibrium and determine whether the equilibrium is stable, asymptotically stable or unstable with respect to the linear approximating equation.
	\item 
Try to use the linear stability/instability obtained in (b) to determine whether each of the equilibria is stable, asymptotically stable or unstable with respect to the nonlinear equation $(*)$.
	\item
If the linear approximation obtained in (b) was not enough to determine the stability of an equilibrium with respect to the nonlinear equation $(*)$, use other methods to determine whether the equilibrium is stable, asymptotically stable or unstable with respect to the nonlinear equation $(*)$
	\item
Sketch the phase portrait for the nonlinear equation $(*)$.
	\end{enumerate}
}


\item
For each of the following systems of differential equations, 
\begin{description}
\item{$\bullet$} rewrite the system in matrix-vector form;
\item{$\bullet$} find general solutions;
\item{$\bullet$} solve the initial value problem with 
initial condition $x_1(0)=-1,x_2(0)=2$;
\item{$\bullet$} sketch the phase portrait, identify the type of each equilibrium, and determine the stability of each equilibrium.
\end{description}

(a) $\displaystyle {dx_1 \over dt} =-4x_1-2x_2,  \quad {dx_2 \over dt}=3x_1-11x_2$

(b) $\displaystyle {dx_1 \over dt} =6x_1+14x_2,  \quad {dx_2 \over dt}=21x_1-x_2$

(c) $\displaystyle {dx_1 \over dt} =7x_1-4x_2,  \quad {dx_2 \over dt}=-2x_1+5x_2$


\item
Consider an initial value problem of differential equations:\\
$x'=2x+3y-3z,\ 
 y'=4x+2y-4z,\ 
 z'=4x+3y-5z,\quad x(0)=-1,\ y(0)=1, \ z(0)=2$.

	\begin{enumerate}
	\item
Rewrite the initial value problem in matrix-vector form.
	\item
Find $x(t),y(t)$, and $z(t)$.
	\end{enumerate}


\item
For each of the following equations, 
\begin{description}
\item{$\bullet$} find general solutions;
\item{$\bullet$} solve the initial value problem with 
initial condition $x_1(0)=-1,x_2(0)=2$;
\item{$\bullet$} sketch the phase portrait, identify the
type of each equilibrium, and determine the stability of each equilibrium.
\end{description}

(a) $\displaystyle {\bf x}' = \bmatrix{ -2 & -13 \cr 1 & 4}{\bf x}$
\qquad
(b) $\left\{
\begin{array}{ll}
dx_1 /dt =x_1+x_2\\
dx_2 /dt = -2x_1-x_2
\end{array} \right.$
\qquad
(c) $\left\{
\begin{array}{ll}
x_1' ={3\over 2}x_1 -4x_2\\
x_2'=5x_1 -{5\over 2}x_2
\end{array} \right.$


\item
Find general solutions of ${\bf x}'=\bmatrix{
5 & -6 & -12 \cr
2 & -4 & -5 \cr
0 & 3 & 2 }{\bf x}$.



