\documentclass[12pt]{article}
\usepackage{graphicx,amsfonts,soul,ulem}
\usepackage[dvipsnames]{xcolor}

\usepackage{hyperref}
% \input setla
% \widelatextwel 
\def\labelenumi{[\theenumi]}
%\pagestyle{empty}

\def\bmatrix#1{\left[\matrix{#1}\right]}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%
%%%%% BEGINNING %%%%%


%%%%%%%%%%%%%%%%%%%%%%

% \def\OFFICEHOURS{TR 2:15pm-3:15pm on BlueJeans Meeting ID 920165011}
% \def\PIAZAAURL{\href{https://piazza.com/gatech/spring2021/math2552gl}{Piazza}}

% \def\ReviewProblems
% {\href{https://gatech.box.com/s/aw5qznprr30kvhnvkrt1ntjv2x788q7d}
% {Review Problems}}


% \def\SEMESTER{Sprnig 2021}
% \def\PROF{Xu-Yan Chen}


\def\PROBONE{Problems [1]-[13]}
\def\PROBTWO{Problems [14]-[35]}
%\def\PROBFINAL{All problems below, if we can cover all the material as planed}
\def\PROBFINAL{All problems below}

%%%%% BEGINNING %%%%%

\vspace*{-2em}


\begin{center}

    \large{MATH 2552 Review Exercises} \\[12pt]

    \normalsize{Many thanks to Dr. Xu-Yan Chen for creating and sharing these review exercises. }
\end{center}

\medskip

\hrule

\medskip


%\line{Classroom: \ROOM \hfil Instructor: \PROF}
%\medskip

%\centerline{\leaders\hrule\hfill\ . \leaders\hrule\hfill\ }
%\medskip
%\pagestyle{empty}


%%%%% Policy %%%%%

\begin{itemize}
	\item This file contains review problems for the whole semester. For a quiz or a midterm, you will only need to use a subset of the problems.

\def\specifyproblems{
	\begin{itemize}
	\item
{\bf Review Problems for Midterm 1:} \PROBONE{}.
	\item
{\bf Review Problems for Midterm 2:} \PROBTWO{}.
	\item
{\bf \hl{Review Problems for the Final:}} \colorbox{yellow}{\PROBFINAL{}.}
	\end{itemize}
}

	\item
The problems below are only meant for your review. 
The real problems on the tests will not be the same problems in this file.
The problems in this file 
do not indicate the whole coverage of the exams
and do not indicate the amount of the required work in the exams. 
You should also review the text, the lecture contents,
the lecture \& studio examples, 
the suggested exercises on the ``Course Schedule" webpage,
and the WeBWork questions. \bf
	\item What to do if need help in solving the problems in this file? \\
\rm
You are very welcome to use the office hours of the instructor and the TAs. You are also encouraged to post questions on Piazza.


% \bf
%	\item{$\bullet$}
% Will the Table of Laplace Transforms (Table 5.3.1 on Page 313 of the text)
% be provided in \EXAMNO?
% 
% \rm
% Yes.

\end{itemize}



 \section*{Exercises}

%%%%% Problems %%%%%
\begin{enumerate}
%%%%% Problems %%%%%

\input{2021Spr/XYC/XYCReview_1}
\input{2021Spr/XYC/XYCReview_2}
\input{2021Spr/XYC/XYCReview_3}
\end{enumerate}

\newpage

%%%%% Answers %%%%%
\section*{Answers}

\begin{enumerate}
\input{2021Spr/XYC/XYCReview_1Ans}
\input{2021Spr/XYC/XYCReview_2Ans}
\input{2021Spr/XYC/XYCReview_3Ans}
\end{enumerate}

 
\end{document}
