\documentclass[12pt]{exam}

\usepackage{graphicx} % allows for graphics
\usepackage{ifthen}  % for if statements 

\newcommand{\sol}{0} %solution =1 or 0

\input{preamble.tex}

% COLORS FOR DIAGRAMS
\definecolor{DarkBlue}{rgb}{0.0,0.0,0.6} % 
% \definecolor{DarkGreen}{rgb}{0.0,0.3,0.0} % 
% \definecolor{DarkRed}{rgb}{0.6,0.0,0.0} % 

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Final Exam Part A}
\newcommand{\TestTime}{}
\newcommand{\Duration}{ }
\newcommand{\Points}{}
% \newcommand{\DueDate}{12:30 PM ET}
\newcommand{\DueDate}{Apr 30, 8:00 pm, ET}


% \usepackage{tikz}
% \usetikzlibrary{shapes,snakes}   
% \usetikzlibrary{arrows,automata}
\usepackage{enumitem} % allows for alpha lettering in enumerated lists

\begin{document}
    

\input{2021Spr/coverpage} % cover page for unproctored exam

\newpage


\InitialsRight

\begin{questions}

    \question[2] Convert the fourth order DE to a first order system. Express your system in the form $\vec x \, ' = A\vec x +\vec b$. 
    $$y^{(4)}- 2 y'' -3ty'+4y = e^{-t}$$
    \vspace{6cm}
    
    \question[1] State whether the following differential equation is linear or non-linear, separable or not separable, and whether it is autonomous or not autonomous. 
    $$t^2\dydt + \sin(t) y = 0$$
    \vspace{2cm}

    \question[4] Determine a suitable form for the particular solution, \(y_p(t)\), if the method of undetermined coefficients is to be used. 
    $$y''+ 15y'+36y = 4\cos(3t)+2e^{-12t}+5t^2$$  
    
    
    \newpage \Initials
    \question[3]  Consider the system $$\vec x \, ' = A\vec x, \quad A = \begin{pmatrix} 1&-2\\2&-3 \end{pmatrix}, \quad \vec x = \begin{pmatrix} x(t)\\y(t)\end{pmatrix} $$ Sketch the phase portrait of the system. Please indicate the direction of motion on your solution curves, and do not forget to label your axes. Please show your work.
    \vspace{5cm}
    
    
    
    
    

    \newpage \Initials
    \question[10] Use the variation of parameters method to identify the general solution to \[\vec{x} \, ' = \left( \begin{array}{rr} -5 & 2 \\ 2 & -2 \end{array} \right) \vec{x}  +  \begin{pmatrix} 60\\ 0 \end{pmatrix} . \]
    Please show your work.
    
    
    \newpage \Initials
    \question[10] Use the Laplace transform to solve the following IVP. Please show your work. 

    $$ y''+ 4y =  g(t), \quad y(0) = 1, \quad y'(0) = 0, \quad g(t) = \begin{cases} 2t & 0 \le t < 3  \\ 6 & 3 \leq t  \end{cases}$$ % B&B 5.7#9 modified
    
    \newpage \Initials
    \question[9] 
    Consider the non-linear system below.
    \[\displaystyle \dxdt = y^2-x^2, \qquad \dydt = 3-y-2x\] % ad hoc  %%% SP21 
    \begin{parts} 
        \part Plot and label the nullclines of the system. Please label your axes. 
        \vspace{7cm} 
        \part Identify all critical points of the system. Show your work. 
        \vspace{7cm}
        \newpage
        \part (Question 7 continued) Compute the Jacobian matrix. For each critical point you identified in part (b), use eigenvalues to classify the critical points according to stability (stable, unstable, asymptotically stable) and type (saddle, proper node, etc). 
    \end{parts}    
    






    \newpage \Initials
    \question[1] One point will be allocated for presentation, neatness, and organization. Please ensure that
    \begin{enumerate}
        % \item your scan is under 5 MB in file size
        \item your work is legible in the scan
        \item your name or initials are at the top of every page
        \item questions are answered in the order in which they were given
        \item during the upload process you have indicated which pages correspond to which question, and made sure that none of your pages are upside down or sideways (you can also change the orientation of the pages when you upload in Gradescope)
    \end{enumerate}
    Ensuring that these criteria are met helps ensure that your exam is graded efficiently and accurately. 
    


    
\end{questions}
    
    Please sign and date the following GT Honor Code statement. \\ 
    
    \vspace{6pt}
    \textbf{Georgia Tech Honor Code}\\
    \GTHonorCode
    
    \begin{center}
    \begin{center}
        \def\arraystretch{0.35}%  1 is the default, change whatever you need
        \begin{tabular}{ b{8cm} b{8cm} }
        \vspace{.5cm} \underline{\hspace{7cm}} & \vspace{.5cm} \underline{\hspace{4.5cm}}  \tabularnewline
        \vspace{6pt} signature & \vspace{6pt} date    
        \end{tabular}
    \end{center}
    \end{center}    
\end{document}











    % \newpage \Initials
    % \question[10] Consider the initial value problem. 
    % $$
    % \vec x \, ' = A\vec x, \quad A = \begin{pmatrix} 5&-1&2\\2&2&2\\2&-1&5\end{pmatrix}, \quad \vec x(0) = \begin{pmatrix} 2\\5\\5 \end{pmatrix}, \quad \vec x = \vec x(t)
    % $$
    % \begin{parts} 
    %     \part Determine the eigenvectors of $A$ and use them to write down the general solution to the system of differential equations. You may use that the eigenvalues of $A$ are $\lambda_1=6$ and $\lambda_2 = 3$, and one of the eigenvalues has a multiplicity of two. \textit{Show your work when computing the eigenvectors: it is ok to check your work with software, but you should show that you can compute eigenvectors by hand. }
    %     \newpage 
    %     \part Use your result from the previous part to solve the IVP. 
    % \end{parts}