\documentclass[12pt]{exam}

\usepackage{amsmath} % allows for align env and other things
\usepackage{graphicx} % allows for graphics
\usepackage{textcomp} % allows for single apostrophe
%\usepackage{enumitem} % allows for alpha lettering in enumerated lists
\usepackage{amsfonts} % for real numbers symbol and other sets

%\usepackage{../spalign}
% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{In-Class Active Learning Worksheet, Sections 2.3 and 2.5}

\usepackage{tikz}

\begin{document}
    
\vspace*{-.5cm}

% COURSE SPECIFIC INFORMATION
\newcommand{\Course}{Math 2552}

\begin{center}
{\Large \TestName 
\\[4pt]
\Course}
\end{center}

\begin{center}    
{\small
\textit{This worksheet will not be collected}
}
\end{center}

\vspace{-.5cm}

\subsection*{Questions}

\begin{questions}

\question     The world population in 2018 is roughly 7.6 billion. 
    
    \begin{parts}
        \part The world population is increasing at a rate of 1.2\% per year. If the growth rate remains fixed at 1.2\%, how long will it take for the population of the world to reach 20 billion people? 
        \part Assume the earth cannot support a population beyond 20 billion people. If the population growth rate is \textbf{also} proportional to the difference between how close the world population is to this limiting value, what is the expression that gives the world population as a function of time? 
    \end{parts}
    
            \newpage

    
\question A system obeys the logistic equation $\frac{dy}{dt} = ry\left(1 - \frac y K \right)$, for $y \in \mathbb R$. 
    
    \begin{parts}
        \part Sketch $f$ vs $y$, identify and classify the equilibrium points of $y$.
        \part For $y \in \mathbb R$ determine whether $y$ is concave up or concave down. 
        \part Use the information in parts (a), (b) to sketch a few integral curves of the DE.
    \end{parts}
    
    \vfill
    

    
    \question A population obeys the DE $y' = a - y^2$, for a parameter $a$. Take a few minutes to solve the following on your own. 

    \begin{parts}
        \part Determine the equilibrium points for any $a\in \mathbb R$. There are three cases.
        \part Sketch the phase lines for each case and classify the critical points. 
        \part For the case when $a>0$, sketch a few solution curves. 
        \part Sketch the location of the critical point as a function of $a$ in an $ay$-plane. 
    \end{parts}

    \vspace{5cm}
    
    
\end{questions}


\end{document}

