\documentclass[12pt]{exam}

\input{../CMPreamble.tex}

% TEST SPECIFIC INFORMATION
\newcommand{\TestName}{Midterm 1}
\newcommand{\TestDate}{on Jan 30 at 8:00 am}
\newcommand{\TestTime}{50 minutes}
\newcommand{\Duration}{50  }
\newcommand{\Points}{35 }


\begin{document}
    
\input{../CMCoverPage}

\newpage

\InitialsRight

\begin{questions}
    
    \question[10] %2.5.11 verbatim 
    Consider the differential equation $\displaystyle \dydt = y(3-y^2) = 3y - y^3$, where $y$ is a real function of $t$. 
    \begin{parts}
        \part State the critical points of the differential equation.  \vspace{0.75cm} 
        \part Draw the phase line, and determine whether the critical points (if any) are stable, semi-stable, or unstable. 
        \vspace{5cm} 
        \part Determine where $y$ is concave up and concave down for $y \ge 0$. 
        \vspace{6cm}
        \part Using results from parts (a) and (b), sketch several solution curves in the $ty$-plane for $y \ge 0$. 
    \end{parts}
    
    
    \newpage \InitialsLeft
    \question[6] Solve the following initial value problem. Solve for $y$ in terms of $t$. 
    $$\displaystyle 0.5\dydt - y = te^{3t}, \quad y(0) = 1$$
    
    
    \newpage \InitialsRight
    
    \question[9] Suppose $A = \spalignmat{2 -1;3 -2}.$  The eigenvalues of $A$ are $\lambda = \pm 1$. % based on 3.3 #13
 	
    \begin{parts} 
    
        \part[4] Determine the eigenvectors of $A$. 
        \vspace{7cm}
        \part[2] Express the general solution of the system $\vec x \, ' = A \vec x$ in terms of real valued functions. 
        \vspace{3cm} 
        \part[3] Sketch the phase portrait of the system. Please include the eigenspaces in your sketch and do not forget to label your axes.      
        \vspace{4cm} 
    \end{parts}
    
    \newpage \InitialsLeft
    
    \question[2] %2.4.2 based on
    State the largest possible interval on which solutions to the IVP are certain to exist. $$t(t-4) \dydt + 7t y = \frac{1}{\sin t}, \quad y(5) = 1$$.
    \vspace{5cm}
    

    
    \vspace{3cm}    
    \question[3] % 3.2.22 verbatim
    Transform the given equation into a system of first order equations. Express your system as an equation that involves a matrix. You do not need to solve the system of differential equations. 
    $$2\dydtt + 0.5 \dydt +8y = 6\sin 2t$$
    
    \vspace{3cm}
    


    
    \newpage \InitialsRight
    

    
    \question[5] % 3.4 13
    Consider the homogeneous system $\displaystyle \vec x \, ' = A \vec x = \spalignmat{\alpha, 1;-1, \alpha}\vec x, \ \alpha \in \mathbb R$. 
    \begin{parts}
        \part Determine the eigenvalues of $A$ in terms of $\alpha$. 
        \vspace{5cm} 
        
        \part Identify the values of $\alpha$ (if any) where the qualitative nature of phase portrait for system changes. 
        \vspace{4cm} 
        
        \part For one value of $\alpha$ that you listed in part (b), sketch the phase portrait for a value of $\alpha$ that is slightly less than the value(s) that you identified. Indicate the value of $\alpha$ that you selected and do not forget to label your axes. 
    \end{parts}
    
%     \newpage 
    
%     \question[5] 
%     The eigenvalues of $A = \spalignmat{3 -2;4 -1}$ are $\lambda = 1 \pm 2i$.  % based on 3.4.1
 	
%   \begin{parts} 
        
%         \part Determine the eigenvectors of $A$. 
%         \vspace{10cm}
        
%         \part Express the general solution of the system $\vec x \, ' = A \vec x$ in terms of real valued functions. 
%         \vspace{3cm} 
        
%         % \part Sketch the phase portrait of the system.  Do not forget to label your axes.      
%         \vspace{4cm} 
        
%     \end{parts}
    
    
\end{questions}
    
% \newpage \LastPage 
% \newpage \LastPage 

\end{document}

